String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-10 2023-1-19/sections/overview.tex
revise syntax in overview

We first construct an automaton for the regular expression $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$. We introduce three registers, say $r_1, r_2, r_3$, to represent the three counting operators.  
%Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting into a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a). 
%Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented. 
%Moreover, $r_0$ is incremented in all the three self-loops. 
Furthermore, the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$. 
A string $w$ is accepted by $\aut_1$ if\denghang{,} when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition. 
Note here\denghang{here to that} we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators. Finally, we construct the third CEFA $\aut_3$ (see Figure~\ref{fig:overview}(c)), where a register $r_4$ is used to denote the length of strings and the accepting condition is $\ltrue$. (See Section~\ref{subsec:regex2cefa} for more details about the construction of CEFA.)
%where the register $r_0$ is used to record the length of strings.

>>>>

We first construct an automaton for the regular expression $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$. We introduce three registers, say $r_1, r_2, r_3$, to represent the three counting operators.  
%Moreover, we introduce another register, say $r_0$, to denote the length of strings. 
Then we first construct a nondeterministic finite automaton (NFA) for $(\Sigma \setminus a)^* (\Sigma \setminus b)^* (\Sigma \setminus c)^*$, then add the updates of registers to transitions, resulting into\denghang{in} a so-called cost-enriched finite automaton (CEFA, see Section~\ref{sec:automaton} for the definition) $\aut_1$,  as illustrated in Figure~\ref{fig:overview}(a). 
%Then we obtain a cost-enriched finite automaton (CEFA) $\aut_1$ that is illustrated in Figure~\ref{fig:overview}(a), where the self-loops around $p_0, p_1, p_2$ represent the first, second, and third counting operator respectively, in which $r_1, r_2, r_3$ are incremented. 
%Moreover, $r_0$ is incremented in all the three self-loops. 
Furthermore, the counting bounds are specified by the accepting condition $1 \le r_1 \le 60 \wedge 1 \le r_2 \le 60 \wedge 0 \le r_3 \le 60$. 
A string $w$ is accepted by $\aut_1$ if\denghang{,} when reading the characters in $w$, $\aut_1$ applies the transitions to update the state and the values of registers, and reaches a final state $q$ in the end, moreover, the resulting values of the three registers, say $v_1, v_2, v_3$, satisfy the accepting condition. 
Note here\denghang{here to that} we represent the counting operators symbolically by registers, instead of unfolding them explicitly. 
Moreover, we construct another CEFA $\aut_2$ for $\Sigma^* c^+$ (see Figure~\ref{fig:overview}(b)), which is actually an NFA, since $\Sigma^* c^+$ contains no (explicit) counting operators. Finally, we construct the third CEFA $\aut_3$ (see Figure~\ref{fig:overview}(c)), where a register $r_4$ is used to denote the length of strings and the accepting condition is $\ltrue$. (See Section~\ref{subsec:regex2cefa} for more details about the construction of CEFA.)
%where the register $r_0$ is used to record the length of strings.
